%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{0}\normalsize
\setlength{\parskip}{0pt}

\begin{document}
	%%%mention the no, time, and venue of the meeting
	\noindent Software Engineering Group Project PG 29 {\bf Hub Room 339} at {\bf 12 pm Friday 18/08/2017}.
	\vspace*{10pt}
	\begin{center}
		\huge Week 4, 1st Meeting Minutes
	\end{center}
	\vspace*{10pt}
	\begin{center}
		\huge Prepared by Ben Winding
	\end{center}
	\begin{center}
		\huge August 18, 2017
	\end{center}
	%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
	\section*{Chair:}
	
	\section{Attendees}
	\begin{itemize}
		\item Sean
		\item Sammy
		\item Pavi
		\item Isaac
		\item Ben
		\item Huy Nguyen
	\end{itemize}
	
	%%%if some students cannot make the meeting due to some reasons, their names should appear here.
	
	
	\section{SPMP Draft}
	Responsibilties for the SPMP
	\subsection*{1. Intro - Sammy}
	\subsubsection*{Purpose/Scope}
	\begin{itemize}
		\item Layout goals clearly
		\item Organise system to deliver goals
		\item Deliverables: robots 
	\end{itemize}

	\subsubsection*{Assumptions and constraints}
	Can be based on SRS
	
	\subsubsection*{Deliverables, Security}
	Can be based on SRS
	
	\subsection*{2. Ref - everyone}
	Everyone update this
	
	\subsection*{3. Definition - everyone}
	Everyone update this

	\subsection*{4. Project Organisation - Issac}
	Reasons why the project is organised like this
	
	\subsection*{5. Risk Management - Sean}
	Risks need to be broken down into cateogries with the following attributes:
	\begin{itemize}
		\item Priorities
		\item Probabilities
		\item Strategy to avoid or mediate
		\item Impact
	\end{itemize}
	
	\subsection*{6. Process Model - Pavi}
	\begin{itemize}
		\item Description of process chosen
		\item Show proccess model diagram
	\end{itemize}
	
	\subsection*{7. Work Plan}
	\subsubsection*{----7.1 Work Activities - John}
	Activity breakdown, Stages for each part of the project, each stage.
	\begin{itemize}
		\item Each stage broken down into features
		\item Estimated time for each feature
	\end{itemize}

	\subsubsection*{----7.2 Milestones - John/Pavi}
	Describe milestones, at least 3.
	\subsubsection*{----7.3 Schedule Allocation - John/Pavi}
	Ghannt charts
	\subsubsection*{----7.4 Resource Allocation - Pavi}
	People roles, distribution of time with robot.
		
	\subsection*{8. Supporting Plans}
	\subsection*{----8.1 Configuration management plan - Issac}
	\begin{itemize}
	\item How we will handle changes to the system.
	\item Using github, with our own system.
	\item Using branches to merge in changes to the system.
	\item Issues tab, Projects Tab.
	\end{itemize}	
	
	\subsection*{----8.2 Documentation plan - Ben}
	\begin{itemize}
	\item Revision processes, SRS review checklist
	\item Documentation formatting
	\item Plan for SRS, SPMP,
	\item Minutes, meeting agenda
	\end{itemize}	
	
	\subsection*{----8.3 Quality assurance plan - Ben}
	\begin{itemize}
	\item Coding standards.
	\item Tracebility of changes.
	\item Software review and inspection process, tested, code review.
	\item Roles of each person
	\begin{itemize}
		\item Pavi - Project Manager
		\item Ben - Documentation Manager
		\item Issac - Testing Manager
		\item Sammy - IT Manager
		\item John - Development Manager
		\item Sean - Quality Manager
	\end{itemize}		
	\end{itemize}		

	\section{Milestone Discussion}
	\subsection*{1st Offical Milestone - Tuesday}
	Robot moving on map, better GUI

	\subsection*{Next Internal Milestone - 12 september}
	Robot moving on map, better GUI
	\begin{itemize}
		\item Detect: NGZ, Tracks, Craters
		\item Obstacles:
		\item Show on Map
	\end{itemize}		
	
	\section{Next meeting}
	
	
	\vspace*{10pt}
	
\end{document}