%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}

\begin{document}
%%%mention the no, time, and venue of the meeting
\noindent Software Engineering Group Project PG 29 {\bf Ingkarni Wardli 462} at {\bf 3:40 pm Tuesday 15/08/2017}.
\vspace*{10pt}
\begin{center}
\huge Week 4, 2nd Client Meeting Minutes
\end{center}
\vspace*{10pt}
\begin{center}
\huge Prepared by Sammy
\end{center}
\begin{center}
\huge August 15, 2017
\end{center}
%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
\section*{Chair: Ben}

\section{Attendees}
\begin{itemize}
\item Chair: Sean
\item Facilitator: John
\item TimeKeeper: Pavi
\item Recorder: Sammy
\item Issac
\end{itemize}

%%%if some students cannot make the meeting due to some reasons, their names should appear here.


\section{Apologies}
\begin{itemize}
\item Ben
\end{itemize}


\section{Q \& A section with Tutor}
\begin{itemize}
\item Strengths and weakness
\item Divided roles
\item Time for each task (need to be specific, like how many hours each member spend)
\item Project models: good
\item What tools the group are using: good
\item Priority requirement needs to be specified.
\end{itemize}

\section{Q \& A section with Client}

\subsection{Robot demonstration}
\begin{itemize}
\item Gui should be able to switch control mode to map display mode with another button.
\item The size of Gui should be bigger.
\item All the program can be run on the laptop.
\item It is fine to have delay.
\item It needs to draw everything found on the map and how to draw it depends on the group.
\item There may be some 3D objects as obstacles and the group can avoid them.
\item It can be treated the robot at the edge if no more than half robot enter specific area.
\item The position of the colour sensor can be changed as long as it works.
\end{itemize}



%%%any schedules for this meeting should go next, each with a separate section.

%%%more issues should make it like the above one.

%%%finally, specifies time of next meeting
\section{Next meeting}
\begin{itemize}
\item Date: 12pm-2pm, Friday, 18 Aug
\item Location: tbd
\item Purpose: List all requirements
\end{itemize}

\vspace*{10pt}

\end{document}