%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}

\begin{document}
%%%mention the no, time, and venue of the meeting
\noindent Software Engineering Group Project PG 29 {\bf Ingkarni Wardli 462} at {\bf 3:40 pm Tuesday 08/08/2017}.
\vspace*{10pt}
\begin{center}
\huge Week 3, 1st Client Meeting Minutes
\end{center}
\vspace*{10pt}
\begin{center}
\huge Prepared by Isaac
\end{center}
\begin{center}
\huge August 8, 2017
\end{center}
%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
\section*{Chair: Ben}

\section{Attendees}
\begin{itemize}
\item Chair: Ben
\item Facilitator: Pavi
\item TimeKeeper: Sean
\item Recorder: Issac
\item Sammy
\item Huy Nguyen
\end{itemize}

%%%if some students cannot make the meeting due to some reasons, their names should appear here.


\section{Q \& A section with Client}
\subsection{The Rover Map}
\begin{itemize}
\item The size of Map is A1 with rectangular border.
\item Obstacles will be represented as either colour line or objects.
\item Map exploration: either shortest path or entire map. This is a client question
\item The Produced map is required to be as accuracy as possible
\item Focus on accuracy and time
\item Time limit: 25 minutes.

\end{itemize}

\subsection{No Go Zones}
\begin{itemize}
\item No go zone is a virtual area and controlled by operator. It will not be showed on the map. 
\item NGZ will be showed on GUI. (Multilayer interface)
\item No consequence to move outside the map as long as the robot can go back.
\item The colour line information will be included into DTD document.
\item EV3 kit: ultrasonic sensor, wifi and bluetooth cables.
\end{itemize}

\subsection{Simulated Terrain and operation of Rover}
\begin{itemize}
\item Mission: Locate landing area, Locate track and be able to go back => To get funding
\item Don't care UI Design.
\item Don't care which UI clients we use (GUI assumes working on computer)
\item Using GUI to command the robot via Wifi or Bluetooth.
 
\end{itemize}

\subsection{Safety}
\begin{itemize}
\item Definition of collision: To cause externel object moving
\item Definition of significant force: The robot's wheels are spinning but no movement.
\item Definition of significant force: Significally demage on a robot and cannot be repaired.
\end{itemize}

\subsection{Millestones}
\begin{itemize}
\item Schedule a millstones and require to demonstrate millstone of project to client
\item E.g Before break: UI demo, basic control. After break: Demo entire robot functions
\end{itemize}

\subsection{General Discussion/Advice}
\begin{itemize}
\item Will test your knowledge of GitHub. Will be tested in command line
\item Preparing our own map as a backup for demonstration
\item Path finding, landing location, UI representation and NGZ handing etc are client questions

\end{itemize}



%%%any schedules for this meeting should go next, each with a separate section.

%%%more issues should make it like the above one.

%%%finally, specifies time of next meeting
\section{Next meeting}
\begin{itemize}
\item Date: 2pm-3pm, Thursday, 10 Aug
\item Location: Level 3-Room 339-Project Room
\item Purpose: Discuss the action after client meeting
\end{itemize}

\vspace*{10pt}

\end{document}