\subsection{The role and responsibilities}
The Software project team consists of Project manager, Documentation Manager, Testing Manager, IT Manager, Development Manager and Quality Manager. The team member’s role and responsibilities are listed as below.

\begin{itemize}
\item \textbf{Name: Pavitterjeet Sidhu}
\item Role: Project Manager
\item Responsibility: \\
1.	Planning all activities throughout the project life cycle, assigning each team member’s duties and monitoring their progress.\\
2.	To organise internal and client meetings.\\
3.	To ensure the project moving along on the right path and meet the deadline.
\item Reason:
Pavi has experience of lending a project. He is familiar with the project’s process model.
\end{itemize}

\begin{itemize}
\item \textbf{Name: Benjamin Winding}
\item Role: Documentation Manager
\item Responsibility:\\
1.	To integrate team member’s documentation work and design project structure.\\
2.	To review team member’s document such as SPMP, SRS and SDD and ensure its the quality with acceptance level.
\item Reason:
Ben has experience of using latex and github. He can identify the issue of our latex file quickly and be familiar with using github to make a file structure.
\end{itemize}

\begin{itemize}
\item \textbf{Name: Kin Leong Lee}
\item Role: Testing Manager
\item Responsibility:\\
1.	To design a set of testing cases and testing scripts for Graphic User Interface and Robot’s functionalities.\\
2.	To review all testing results and write a testing report.
\item Reason:
Kin has experience of working in IT company and performed difference testing for software product. He is familiar with the testing process and building testing script.
\end{itemize}

\begin{itemize}
\item \textbf{Name: Xiaoshan Chen}
\item Role: IT Manager
\item Responsibility:\\
1.	To be responsible for the connection between EV3 robot and remote system.\\
2.	To handle and solve all the issues about using IDE.
\item Reason:
Shan has experience of working a IT company and responsible for IT support. She can handle difference IT problems and has experience of using intellij.
\end{itemize}

\begin{itemize}
\item \textbf{Name: Phan Huy Nguyen}
\item Role: Development Manager
\item Responsibility:\\
1.	To design the program structure and develop coding policies.\\
2.	To review all team member’s coding work including GUI, robot movement, robot sensors and path finding.
\item Reason:
Phan has software company working experience. He is familiar with the industry standard of coding.
\end{itemize}

\begin{itemize}
\item \textbf{Name: Sean Hennessy}
\item Role: Quality Manager
\item Responsibility:\\
1.	To identify all the risks of project throughout project life cycle.\\
2.	To plan the strategic to solve the project issues and ensue all the submitted works following the standard and good quality.
\item Reason:
Sean has experience of making budget plan for the project. He also studied project management course and has a skill to identify the risks of project.
\end{itemize}

The detail responsibilities for each team member is shown on Table1:

\begin{table}[]
	\centering
	\caption{Responsibilities table}
	\label{my-label}
	\begin{tabular}{|l|l|l|l|l|l|l|}
		\hline
		Tasks/Members                                        & Pavi & Ben  & Issac & Shan & Phan & Sean \\ \hline
		\multicolumn{7}{|l|}{\textbf{Management}}                                                       \\ \hline
		Planning and Schedule                                & A\&R & I    & I     & I    & I    & I    \\ \hline
		Risk Management                                      & I    & I    & I     & I    & I    & A\&R \\ \hline
		Meeting Agenda                                       & R\&A & R    & R     & R    & R    & R    \\ \hline
		Meeting minutes                                      & R\&A & R    & R     & R    & R    & R    \\ \hline
		\multicolumn{7}{|l|}{\textbf{Documentation}}                                                    \\ \hline
		Documents (SRS, SPMP, SDD)                           & R    & R\&A & R     & R    & R    & R    \\ \hline
		Review Documents                                     & I    & R\&A & I     & I    & I    & I    \\ \hline
		\multicolumn{7}{|l|}{\textbf{Connection Management}}                                            \\ \hline
		Establish connection between robot and remote system & I    & I    & R     & R\&A & I    & I    \\ \hline
		Implement plugin to IDE and make it work             & I    & I    & I     & R\&A & I    & R    \\ \hline
		\multicolumn{7}{|l|}{\textbf{Software Development}}                                             \\ \hline
		Developing GUI                                       & R    & I    & R     & I    & R\&A & R    \\ \hline
		Developing Robot functionalities                     & I    & R    & I     & R    & R\&A & I    \\ \hline
		Integration                                          & R    & R    & I     & I    & R\&A & I    \\ \hline
		\multicolumn{7}{|l|}{\textbf{Testing}}                                                          \\ \hline
		Building Testing script                              & I    & R    & R\&A  & I    & R    & I    \\ \hline
		Acceptance Test                                      & R    & I    & R\&A  & R    & I    & R    \\ \hline
	\end{tabular}
\end{table}
\begin{itemize}
\item R(Responsible): Team member is responsible for this task
\item A(Accountable): Team member is responsible to assign the work to each group member
\item I(Informed): Team member will be informed when the task is completed\\
(A Guide to the Project Management Body of Knowledge 2013 p.262)
\end{itemize}